---
title: "Simulating Spikes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulating-Spikes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Simulating Spikes is a package, which simulates spikes sequences from 1D inhomogeneous point processes. The simulated spikes could be used as surrogate data when obtaining experimental data is difficult if not impossible. 

In this vignette, we'll use the SimSpikes package to create a plethora of spike sequences with different properties.

To begin, we need to explain the model behind the point process. Our model is fully defined by the intensity function $x(t)$, and choice of distribution with parameter/s $\theta$.

$$f(t,s|x,\theta) = x(t)p(X(s,t)|\theta)$$
```{r setup, include = FALSE}
library(SimSpikes)
```


An example of a single spike sequence simulated in $[0,20]$, where the intensity at time $t$ is given by $x(t) = cos(t/5)+1.5$, and the ISI is a Gamma with parameter $(5,5)$ and no refractory period. 
```{r, fig.width= 7, fig.height=7}
end.time = 20 
t <- seq(0,20,0.01) ; int.fn <- cos(t/5) + 1.5
ISI.type = 'Gamma' ; hyper = 5 ; T.min = NULL
set.seed(12)
simulate_spikes(end.time, int.fn, hyper, steps =1000, T.min = T.min, ISI.type = "Gamma",sequences = 1)
```
